---
title: "Exploratory Data Analysis"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: xelatex
---

## Load Required Libraries
```{r, error=FALSE, warning=FALSE, message=FALSE, results='hide'}
library(dplyr)
library(insight)
library(knitr)
library(kableExtra)
library(ggplot2)
library(tidyverse)
library(corrplot)
library(patchwork)
```

## Load Data & Inspect Variables
```{r}
# Read the data
data <- read.csv("Credit.csv")
# Check the number of observations and number of variables
n <- nrow(data)
m <- ncol(data)
n
m
# Check the data
kable(head(data[, 1:8]), format = "latex", align=rep("c", 8))
kable(head(data[, 9:14]), format = "latex", align=rep("c", 6))
kable(head(data[, 15:21]), format = "latex", align=rep("c", 7))
# Check invalid or missing values
anyNA(data)
# Check the data type of each column
sapply(data, class)
```

As we can see from the above outputs, there is no NaN values so the data is clean.
And all of the columns are of type integer. Some of them are quantitative variable while some of 
them are qualitative variables. Here is a summary of the variables:

* status: status of the debtor's checking account with the bank (categorical)
* duration: credit duration in months (quantitative)
* credit_history: history of compliance with previous or concurrent credit contracts (categorical)
* purpose: purpose for which the credit is needed (categorical)
* amount: credit amount in DM (quantitative; result of monotonic transformation; actual data and type of transformation unknown)
* savings: debtor's savings (categorical)
* employment_duration: duration of debtor's employment with current employer (ordinal; discretized quantitative)
* installment_rate: credit installments as a percentage of debtor's disposable income (ordinal; discretized quantitative)
* personal_status_sex: combined information on sex and marital status (categorical)
* other_debtors: is there another debtor or a guarantor for the credit? (categorial)
* present_residence: length of time (in years) the debtor lives in the present residence (ordinal; discretized quantitative)
* property: the debtor's most valuable property (ordinal)
* age: age in years (quantitative)
* other_installment_plans: installment plans from providers other than the credit-giving bank (categorical)
* housing: type of housing the debtor lives in (categorical)
* number_credits: number of credits including the current one the debtor has (or had) at the bank (ordinal; discretized quantitative)
* job: quality of debtor's job (ordinal)
* people_liable: number of persons who financially depend on the debtor (binary; discretized quantitative)
* telephone: is there a telephone landline registered on the debtor's name? (binary)
* foreign_ worker: is the debtor a foreign worker? (binary)
* credit_risk: has the credit contract been complied with (good) or not (bad)? (binary)

We can see that the **quantitative variables** include duration, amount and age, while **qualitative variables** include
status, credit_history, purpose, savings, employment_duration, installment_rate, personal_status_sex, other_debtors, present_residence, property, other_installment_plans, housing, number_credits, job, people_liable, telephone, foreign_worker and credit_risk.

## Univariate Analysis & Visualization

First we will perform univariate analysis on each of the variables and look at their distribution. Here is the 
summary statistics:
```{r}
quant_vars <- c("duration", "amount", "age")
qual_vars <- c("status", "credit_history", "purpose", "savings", "employment_duration",
               "installment_rate", "personal_status_sex", "other_debtors", "present_residence", 
               "property", "other_installment_plans", "housing", "number_credits", "job", "people_liable",
               "telephone", "foreign_worker")
summary(data[, quant_vars])
```

Next, let us check the histograms of the quantitative variables:
```{r results='hide'}
par(mfrow=c(1,3))
lapply(quant_vars, FUN=function(c)
  hist(data[, c], xlab=c, main=paste("Histogram of", c)))
```

Then, let us check the barplots of qualitative variables:
```{r results='hide'}
par(mfrow=c(2, 3))
lapply(qual_vars, FUN=function(c)hist(data[, c], xlab=c, main=paste("Histogram of", c)))
```

After checking the histograms and barplots, we will check the boxplots of the quantitative variables.
Here we will not check barplots for qualitative variables because it only makes sense to examine the median,
first and third quartiles and maximum value for quantitative variables. 
```{r}
g1 <- ggplot(data, aes(x = amount)) + geom_boxplot(fill="#FEF8DD") 
g2 <- ggplot(data, aes(x = duration)) + geom_boxplot(fill="#E1F8DC") 
g3 <- ggplot(data, aes(x = age)) + geom_boxplot(fill="#ACDDDE") 
g1 + g2 + g3
```

From the above box plots, we can see that there are a few outliers for the variable amount. If 
we look at the histogram of variable amount, we can see that it is a right skewed distribution
with a long right tail, which results in these outliers.

For binary variables people_liable, telephone, foreign_worker and credit_risk, we can calculate and 
interpret the sample odds:
```{r}
binary_var <- c("Statistics", "people_liable", "telephone", "foreign_worker", "credit_risk")
odds <- c("Sample Odds")
for (var in binary_var[2:5]) {
  if (var == "credit_risk") {y <- sum(data[, var] == 1)}
  else {y <- sum(data[, var] == 2)}
  n <- length(data[, var])
  odds <- append(odds, round(y / (n - y), 2))
}
kable(data.frame(t(odds)), col.names = binary_var, format = "latex") %>% 
  kable_styling(position = "center", latex_options = "hold_position") %>% row_spec(0, bold = TRUE)
```

Based on our sample, the estimated probability of a person to have good credit
is 2.33 times as likely as having a bad credit. Similarly, the estimated probability
of a person to have a telephone landline registered on his/her name is 0.68 times 
as likely as not having such a telephone landline.

## Multivariate Analysis
First, let us look at the correlation plots of the quantitative variables.
```{r}
corrplot.mixed(cor(data[quant_vars]), lower='number', upper='ellipse', order='AOE')
```

From the above correlation plot, we can see a strong correlation between amount and duration.